A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
revise a typo

Since ${\rm Var}(\Delta') < 4\epsilon^2 k^2 m $, we can assume the maximum value of $X_{\xi}$ is
proportional to the standard deviation of $\Delta'$, i.e. $\epsilon$. Thus, we can assume
$\zeta=\epsilon C$, where $C$ is a constant factor.

>>>>

Since ${\rm Var}(\Delta') < 4\epsilon^2 k^2 (m - \frac{m(m-1)}{N-1}) $, we can assume the maximum value of $X_{\xi}$ is
proportional to the standard deviation of $\Delta'$, i.e. $\epsilon$. Thus, we can assume
$\zeta=\epsilon C$, where $C$ is a constant factor.
